Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-21 lloveras_2020.tex
nuevos graficos

\author[addressref={},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}\lnm{Sachdeva}\orcid{1}}

\author[addressref={},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}\lnm{Manchester IV}\orcid{2}}

\author[addressref={},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}\lnm{Van der Holst}\orcid{3}}

@@

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel). Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
\label{rpoint}
\end{center}
\end{figure}

@@

For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

@@

\begin{figure}%[h]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}

>>>>

\author[addressref={aff1,aff3,aff2},corref,email={cmaccormack@iafe.uba.ar}]{\inits{C.}\fnm{Cecilia}~\lnm{Mac Cormack}}

\author[addressref={aff4},corref,email={nishthas@umich.edu}]{\inits{N.}\fnm{Nishtha}~\lnm{Sachdeva}\orcid{1}}

\author[addressref={aff4},corref,email={chipm@umich.edu}]{\inits{W.}\fnm{Ward}~\lnm{Manchester IV}\orcid{2}}

\author[addressref={aff4},corref,email={bartvand@umich.edu}]{\inits{B.}\fnm{Bartholomeus}~\lnm{Van der Holst}\orcid{3}}

@@

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_cr2208_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel). Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
\label{rpoint_demt}
\end{center}
\end{figure}

@@

%For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were separated into the coronal {regions described in Section \ref{regions} and summarized in Table \ref{tabregions}}. For each field line, the data points of electron density and electron mean temperature versus height were fitted to the functions given by Equations 5 and 6 of Section \ref{trace}. As a result, the footpoint electron density $N_0$ and scale height $\lN$ were computed for each field line, as well as the temperature gradient $a=\textrm{d}T_m/\textrm{d}r$, and the height-averaged (along the loop) electron mean temperature $\aTm$. As the DEMT technique studies only coronal conditions, \textit{i.e.} above height $r\approx 1.025\,\mrsun$, the exponential fit to the electron density data versus height was used to compute the {coronal base electron density} here defined as $\NCB\equiv N_e(r=1.025\,\mrsun)$. Also, for each field line the coronal base magnetic field strength $B_{\rm CB}\equiv B(r=1.025\,\mrsun)$ and its height-averaged value along the loop $\left<B\right>$ were also computed.

@@

\begin{figure}%[h]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_cr2082_up_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_cr2208_up_Rpoint-map.eps}
\caption{Same as Figure \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2082_1105.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Ne_demt_awsom_2208_1105.eps}
\caption{Longitude-averaged of DEMT (blue) and AWSoM (red) results at $1.105\,\mrsun$. On the left CR2082 and on the right CR2208, the vertical black lines indicates the longitude-averaged latitudes of the open/close magnetic boundaries.}
\label{perf_lon_ne}
\end{center}
\end{figure}

\begin{figure}%[ht!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995.eps}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995.eps}
\caption{Longitude-averaged of radial wind speed at $6\,\mrsun$ given by AWSoM.}
\label{perf_lon_vr}
\end{center}
\end{figure}
